Tracking Examples

### 2023-08-14 illustrations/tracking-examples.Rmd
update references

```{r}
building_pl <- ggplot(building_df) +
  geom_sf(linewidth = .5, alpha = 0, lwd = 0) +
  scale_fill_discrete(na.translate = F) +
  scale_x_continuous(breaks = seq(-20000, 20000, 1000)) +
  scale_y_continuous(breaks = seq(-20000, 20000, 1000)) +
  guides(fill = "none")

@@

examples_pl
```

>>>>

```{r}
building_pl <- ggplot(building_df) +
  geom_sf(linewidth = .5, alpha = 0, color = NA) +
  scale_fill_discrete(na.translate = F) +
  scale_x_continuous(breaks = seq(-20000, 20000, 1000)) +
  scale_y_continuous(breaks = seq(-20000, 20000, 1000)) +
  guides(fill = "none")

@@

examples_pl
save_plot(examples_pl, pdf_file = "tracking-examples.pdf", w = 16, h = 12)
```
